Formalization of Network Flow Algorithms

### 2017-03-02 paper/root.tex

	\nextgroupplot[
    	title={Random Dense Graphs},
    	title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {0.1,2,5,10,15},
      xticklabels = {$1k$, $1.1k$, $1.2k$, $1.3k$, $1.4k$}, 
      yticklabels = {$0.1$,$2$,$5$,$10$,$15$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={Goldberg Bad Case (Washington)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {3000, 6000, 9000, 12000, 15000},
      ytick = {0.1,1,10,50,100},
      xticklabels = {$3k$, $6k$, $9k$, $12k$, $15k$},
      yticklabels = {$0.1$,$1$,$10$,$50$,$100$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,22000,25000,30000},
      ytick = {0.1,1,5,10,20},
      xticklabels = {$16k$, $19k$, $22k$, $25k$, $28k$}, 
      yticklabels = {$0.1$, $1$,$5$,$10$,$20$}, 
      smooth,
      cycle list name = black white
	]

>>>>

	\nextgroupplot[
    	title={Random Dense Graphs},
    	title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {0,1000,1100,...,1400},
      ytick = {0.1,2,4,8,12},
      xticklabels = {$1k$, $1.1k$, $1.2k$, $1.3k$, $1.4k$}, 
      yticklabels = {$0.1$,$2$,$4$,$8$,$12$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={Goldberg Bad Case (Washington)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {3000, 6000, 9000, 12000, 15000},
      ytick = {0.1,1,10,40,80},
      xticklabels = {$3k$, $6k$, $9k$, $12k$, $15k$},
      yticklabels = {$0.1$,$1$,$10$,$40$,$80$}, 
      smooth,
      cycle list name = black white
	]

@@

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,22000,25000,30000},
      ytick = {0.1,1,4,8,16},
      xticklabels = {$16k$, $19k$, $22k$, $25k$, $28k$}, 
      yticklabels = {$0.1$, $1$,$4$,$8$,$16$}, 
      smooth,
      cycle list name = black white
	]
